%=================20==================40==================60==================80
%                      Chinese-English App. Methodology
%=================20==================40==================60==================80
\documentclass{article}
%==============================================================================%
%                                  Packages
%==============================================================================%
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
%==============================================================================%
%                                  Commands
%==============================================================================%
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
%==============================================================================%
\title{Chinese-English App. Methodology}
\author{Chris Zhang and Shane Flynn}
\date{March 2020}
\begin{document}
%==============================================================================%
\section*{To Do List}
Development is broken into short-term and long-term directions.
We are interested in optimizing our methodology and are eager to hear from
people with linguistics and education backgrouds to comment on our approach

\subsection*{Short-Term Goals}
\begin{itemize}
  \item  We need a working prototype, be able to open an indepedent window and
  call an audio file.
  \item Scoring scheme for individual cards and user interface.
  \item Optimal number of cards for the learning decks.
  \item Graphic visualization for tones on each card.
  \item Pinyin and kanji for each card.
  \item Statistics on each card and on user usage.
  \item Main deck.
\end{itemize}

\subsection*{Long-Term Goals}
\begin{itemize}
  \item Make a database for the audio files.
  \item English recordings for mandarin speakers to practice english
  pronunication.
  \item Simplified kanji.
\end{itemize}

\section*{Vocabulary Tables}
Current vocabulary available organized by level

\section*{Database}
A database is simply an organized collection of related information.
DBMS stands for database management systems which is software designed for
creating and maintaining databases.
Generally when you work with a database you are creating, reading from, updating,
and deleting information.
A DBMS provides these 4 major functions.

There are two major types of databases, SQL (relational) and non-relational
(noSQL).
Relational databases are the most common, they create tables and store the
data within these tables.
noSQL are simply anything else.
mySQL and Oracle are relational DBMS and use SQL to interact with the database.
mongoDB, apache are examples of noSQL DBMS.

SQL is standardized, across platforms there is slight changes in syntax but
equivalent structure, the same is not true for noSQL methods.

Given our data space will not be changing (name-english name-chinese Pinyin
tones audio) we do not need to use object-oriented methods for the database and will
simply use a relational database.
For development SQLite seems ideal as it can be used directly from standard
python library and it does not require us to make a server.
We will have 1 file with tables and the tables contain the data, our entire
database is just one file.

In the future we could imagine increasing the dataspace to have user information
for development we will just focus on the application itself.

Another option would be a non-relation database like JSON where you store
all your information in a file (something like a dictionary in python).


\section*{Card Selection Implementation}
The choice of which card to test is crucial.

\end{document}
